Design Document for R Package glmm

### 2016-06-30 NewDesignDoc/DesignDocGLMM.tex
changed to qr decomp
qr decomp in vcov, summary, confint

To do steps:
\begin{enumerate}
\item Remember how to do QR decomp (or some other stable matrix decomposition to stable invert the matrix)
\item Calculate $\hat{V}$ and the rest of the MCSE calculation in R
\item Change the  $\hat{V}$ calculation to C
\end{enumerate}

>>>>

To do steps:
\begin{enumerate}
\item Remember how to do qr decomp (stably invert the matrix with qr.solve)
\item Calculate $\hat{V}$ and the rest of the MCSE calculation in R
\item Change the  $\hat{V}$ calculation to C
\end{enumerate}

\subsubsection{Cholesky Decomposition for Matrix Inversion}
Cholesky decomposition takes a symmetric, positive definite matrix and decomposes it into $LL'$, where $L$ is a lower triangular matrix and $L'$ is the transpose of L (so it's upper triangular). Triangular matrices are easy to solve using \texttt{backsolve} in R. For example, if you have the hessian \texttt{hess} and want to get the variance covariance matrix, then do 
\begin{verbatim}
cho <- chol(hess)
uinv <- backsolve(cho, diag(nrow(cho))
vcov <- uinv %*% t(uinv)
\end{verbatim}
